%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
\label{chap:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapterstart

% Overall problem
%  and why is it relevant 
%  relevant to which target group
% key questions to answer
% your approach, the method (survey, prototype, user tests, ...)
% one/two hypotheses (idea of solution)

Your text here\ldots 
\TODO{Describe the kind of problem at hand? The problem is relevant in which 
context? What does not work well at the moment? 
What do people need? Describe the background, the prerequisites for your 
work. Optionally, add terms and definitions whenever they might not be clear 
to a fellow student. test ~\parencite{Brooks:1975} }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Statement}\label{sec:problem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Your text here\ldots 
\TODO{What is the overall problem? Give examples. Motivate! Compared to 
existing solutions for the problem at hand, why does someone need a better, 
faster, and somewhat different one?
test }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Questions}\label{sec:rq}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Your text here\ldots 
\TODO{Focus on one or two main research questions and detail on them.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hypothesis}\label{sec:hypothesis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


Your text here\ldots 
\TODO{State a hypothesis -- a rough idea -- of how you think a solution might 
look like. Explain, how to possibly solve a given problem.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Method}\label{sec:method} % Materials and Methods
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Your text here\ldots 
\TODO{Your structured, academic approach\footnote{Find an extensive 
explanation of how to write a \emph{Method} section 
at \url{http://www.mrcophth.com/publishorperish/methods.html}.} to find a 
solution. When you needed (large) data sets for you work, explain how you 
collected and filtered raw data. 
For the validation (see Section \nameref{chap:evaluation}~\ref{chap:evaluation}) 
you want to describe the criteria for objective measurement already here.
}


% selected methods (experiment, survey, case study, ...):
% 
%  typical analytic settings: "deductive"
%   	(literature survey)
% 		analysis (according to your previously specified criteria) 
%  typical experimental settings: "inductive"
%  		compare system/situation x and y
%  		new combination of a and b leads to c
%		
%  => 
%  design your experiment
%   decide how to observe (measure) and collect (and process) data
%   prototype implementation = "proof-of-concept
%   study process or software product
% ...
%  often, you might include:
%    user testing, heuristic evaluations





\chapterend

